---
title: "Assignment_2"
author: "Dan Boguslavsky"
date: "5/12/2020"
output: html_document
---
```{r}
rm(list=ls())
```

```{r Question 1}
#install.packages('rattle.data')
library('rattle.data')
wine<-rattle.data::wine
?wine
```

#1.a.
```{r Q-1,a}
plot(Flavanoids~Phenols,data = wine)
```
It seems that indeed, Flavanoids and Phenols have some linear relationship between them.

#1.b.
The model: Flavanoids = β0 + β1*Phenols + error
in this model we assuming that the amount of Flavanoids affected by the amount of Phenols.
Additionaly we assuming all of the basic assumption of the linear regretion.

#1.c.
We want to minimize the sum of residual squares. So to get those expressions we need to deriviate the sum by β0 and β1 and equal to '0',
and then solve the equations, and find β0 and β1.

There are few assumptions we must assume to make those calculations:
1. Independence - we assume that the residuals are independent.
2. Centered - we assume that the Expected value of the resudials is '0'. (E(res) = 0).
3. Normality - we assume that the resudials are distrebured normally (res ~ N(µ,Var)).

#1.d.
```{r Q-1,d}
lm.Flavanoids.Phenols<- lm(wine$Flavanoids~wine$Phenols)
#Estimation resaults:
predict(lm.Flavanoids.Phenols)
#Plot + regression line:
plot(Flavanoids~Phenols,data = wine)
abline(coef(lm.Flavanoids.Phenols)[1:2])
```

#1.e.
```{r Q-1,e}
#Slope coefficient:
coef(lm.Flavanoids.Phenols)[2:2]
summary(lm.Flavanoids.Phenols)
```
The slope coefficient is significant. We base it on the t-value of the effect - which is 22.82.
That indicates a very significant effect. We can also be assisted by the "star" code on the right of the "summary" command - "***" means significance level of under 0.001% for the effect to be insignificant.

#1.f.
```{r Q-1,f}
plot(density(lm.Flavanoids.Phenols$residuals),main = "Residuals",col="red")
legend("topright", legend=c("syntatic norm dist", "residual dist"),
           col=c("black","red"),lty=1, cex=0.7)
set.seed(256)             
lines(density(rnorm(1:178,0,0.5)))
shapiro.test(lm.Flavanoids.Phenols$residuals)
```

We add normal distrabiotion line to compare it with the residual distrecution.
Additionaly we add shapiro-wilk test in order to verifay the segnigicant the residual distrecution is normal distrebiotion.
You can noticte the simularity in the plot and the p-value of the shapiro-wilk test is 0.0003786 (very very segnigicant).

#1.g.
```{r Q-1,g}
#β0, β1 calculation:
numerator<-c()
denominator<-c()
residuals.vec<-c()
mean_x<-mean(wine$Phenols)
mean_y<-mean(wine$Flavanoids)
for(i in 1:NROW(wine)){
  x_i<-wine$Phenols[i]
  y_i<-wine$Flavanoids[i]
  numerator<-c(numerator,((x_i-mean_x)*(y_i-mean_y)))
  denominator<-c(denominator,((x_i-mean_x)^2))
}#close_for
b.1 <-sum(numerator)/sum(denominator)
b.0 <- mean_y - b.1*mean_x
#Residuals calculation:
for(i in 1:NROW(wine)){
  y_i<-wine$Flavanoids[i]
  x_i<-wine$Phenols[i]
  y_hat<-x_i*b.1+b.0
  res<-((y_i-y_hat)*(y_i-y_hat))
  residuals.vec<-c(residuals.vec,res)
}#close_for
RSS <-sum(residuals.vec)
#R_squ calculation:
numerator<-c()
denominator<-c()
for(i in 1:NROW(wine)){
  y_i<-wine$Flavanoids[i]
  x_i<-wine$Phenols[i]
  y_hat<-x_i*b.1+b.0
  numerator<-c(numerator,((y_i-y_hat)^2))
  denominator<-c(denominator,((y_i-mean_y)^2))
}#close_for
R_sqr <-(1-(sum(numerator)/sum(denominator)))
b.0
b.1
RSS
R_sqr

#1.
print("#our computaion:")
b.0
print("#from summary(lm):")
lm.Flavanoids.Phenols$coefficients[1]

#2.
print("#our computaion:")
b.1
print("#from summary(lm):")
lm.Flavanoids.Phenols$coefficients[2]

#3.
print("#our computaion:")
RSS
print("#from summary(lm):")
sum(lm.Flavanoids.Phenols$residuals^2)

#4.
print("#our computaion:")
R_sqr
print("#from summary(lm):")
summary(lm.Flavanoids.Phenols)$r.squared
```
We can see that our computaions are the same as the summary of the model presents.

#1.h.
```{r Q-1,h}
library("ggplot2")
ggplot(wine, aes(x=Flavanoids, y=Phenols, color = Type)) + geom_point()
```